XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-25 talk/icooolps2011/paper.tex
add line numbers to the trace about where the operations originate from
move conclusion bits around

The trace would look like in Figure~\ref{fig:trace1}. In this example, the
attribute \texttt{a} is found on the instance, but the
attributes \texttt{b} and \texttt{c} are found on the class. The trace indeed contains
five calls to \texttt{dict.get}, which is slow. To make the language efficient
using a tracing JIT, we need to find a way to get rid of these dictionary
lookups somehow. How to achieve this will be topic of
Section~\ref{sec:putting}.

@@

\subsection{Conclusion}

In this section we presented two hints that can be used in the source code
of the interpreter. They are used to influence what the optimizer does with the
trace. The examples given here are a bit too small, the next
section gives a worked-out example that puts all the pieces together.

@@

\subsection{Conclusion}

In this section we saw how to use \texttt{purefunction} and \texttt{promote} to make a
small but still relevant dynamic object model no longer use any dictionary lookups
after tracing. Instead a number of guards are inserted into the
trace to check whether the assumptions about the objects are still true. This
makes operations on objects seriously faster.

@@

>>>>

The trace would look like in Figure~\ref{fig:trace1}. In this example, the
attribute \texttt{a} is found on the instance, but the
attributes \texttt{b} and \texttt{c} are found on the class. The numbers line
numbers in the trace correspond to the line numbers in
Figure~\ref{fig:interpreter-slow} where the traced operations come from. The
trace indeed contains
five calls to \texttt{dict.get}, which is slow. To make the language efficient
using a tracing JIT, we need to find a way to get rid of these dictionary
lookups somehow. How to achieve this will be topic of
Section~\ref{sec:putting}.

@@

@@

@@

In this paper we presented two hints that can be used in the source code of an
interpreter written with PyPy. They are used to influence what the optimizer
does with the trace. We also showed how a small but still relevant dynamic
object model can use these hints to no longer use any dictionary lookups after
tracing. Instead a number of guards are inserted into the trace to check whether
the assumptions about the objects are still true. This makes operations on
objects seriously faster.

XXX
